### 2023-07-19 main.tex
Clean up II
In blue the parts that could not be need now

@@

%Then, we obtain the correspondent transfer matrix as
%\begin{equation}
%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
%\end{equation}
%where
%\begin{equation}
%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
%\end{equation}
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
\begin{equation}
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}

@@

\paragraph{Genearlization to $N$ species:} we can generalize the eigenvector formula for arbitrary number of species $N>2$ by writing
	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
Denoting by
A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=\,k_{q}\}}\right)
\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
Condition \eqref{cond4} becomes
\begin{equation}\label{cond4General}
	G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
Arguing as in the case $N=3$ we observe that 
		A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=k_{q}\}}\right)
	\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
therefore \eqref{cond4General} is fulfilled. Again, the equivalent of conditions \eqref{cond1}, e\eqref{cond5} and \eqref{cond6} are trivially satisfied. The equivalents of conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{j}(x)$ are rising operators for all $j\in \{2,\ldots,N\}$. 
We show that, if these previous conditions are satisfied, then the $|\Psi^{\Delta}_{m_{2},m_{3}}\rangle$ are indeed eigenvalues of $H^{''}$. 
T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0} 
\\&+\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}+1}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots +
\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}+1}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
we replace $k_{i}\to k_{i}+1$ $\forall i\in\{2,\ldots,N\}$ in the proper summation. Then,
T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{2}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2}-1,\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots
\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}(2x+N)B_{N}(x)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}-1}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\Delta_{2}^{m_{2}+1}\sum_{a_{3}=0}^{m_{3}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{3}^{k_{3}}\Delta_{N}^{k_{N}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{m_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots +
\Delta_{N}^{m_{N}+1}\sum_{a_{2}=0}^{m_{3}}\ldots\sum_{a_{N-1}=0}^{m_{N-1}}\Delta_{3}^{k_{2}}\Delta_{N-1}^{k_{N-1}}(2x+N)B_{2}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
We use prperties \eqref{SecondProperty} and \eqref{FirstProperty}:
T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=T_{0}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}T_{0}(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots +
\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left[\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)I-T_{0}(x)\right]G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
then
T_{\Delta}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle&=
\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle
\sum_{a_{2}=1}^{m_{2}}\ldots\sum_{a_{N}=0}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)(x)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\\&+\ldots+	\sum_{a_{2}=0}^{m_{2}}\ldots\sum_{a_{N}=1}^{m_{N}}\Delta_{2}^{k_{2}}\ldots \Delta_{N}^{k_{N}}\left(\Lambda_{m_{2},m_{N}}(x)+\epsilon\right)G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
\Lambda_{m_{2},\ldots,m_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle

>>>>

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N\\
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1\\
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=N(I^{tot}+e_{NN}^{tot})+e_{NN}^{tot}(2e_{NN}^{tot}+I^{tot})-\sum_{j=1}^{N-1}e_{jj}^{tot}-2N\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{k=1}^{N-1}\left\{e_{NN}^{tot}-\sum_{j=1}^{N-1}e_{jj}^{tot}+\sum_{j=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right\}
\\&=
(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
we also introduce 
\begin{equation}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

\subsection{The non local transformation}
We define the equilibrium Hamiltonian as
	H^{0}=H_{left}^{0}+H_{bulk}+H^{''}_{right}
		H_{left}^{0}=e_{NN}^{1}-\mathbbm{1}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}^{L}
Therefore we have that
	H^{''}=H^{0}+H^{B}
	H^{B}=\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}
We look for a matrix $W$ such that 
\begin{equation}\label{GoalWH}
	H^{''}W=WH_{0}
We have that 
	\left[H_{0},Q^{0}_{2L}\right]=0\qquad \left[H^{''},Q_{2L}\right]=0
thus it is enough to look for a matrix $W$ such that 
\begin{equation}\label{GoalWQ}
	Q^{2L}W=WQ_{2L}^{0}
To find a matrix $W$ such that \eqref{GoalWH} is fulfilled we use the \textit{resolvent operator} defined as
	R(z,H):=\left(zI-H\right)^{-1}
where $z$ must be in the resolvent set, i.e. the subset of $\mathbb{C}$ such that the resolvent is well defined. 
The above equation implies that 
	(z-H)R(H,z)=1
In order to be well defined we must $z$ must not be an eigenvalue of $H$ (and thus of $H_{0}$). We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We take $z=\Lambda_{\bm{m}}+\epsilon$ 
	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)=1
We multiply both sides by $|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|$
	(\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We sum over all possible $m$ 
	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We multiply both sides by $\epsilon$ 
	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
We take the limit for $\epsilon\to 0$ on both sides 
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
Observe that 
	\lim_{\epsilon\to 0}\left(\Lambda_{\bm{m}}+\epsilon-H\right)=\left(\Lambda_{\bm{m}}-H\right)<\infty
and using the following power expansion
\begin{equation}\label{veryUsefulSeries}
	(A-B)^{-1}=\sum_{n=0}^{\infty}(A^{-1}B)^{n}A^{-1}
we have that for each $\bm{m}$ 
		&\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}H\right)^{n}(\Lambda_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\Lambda_{\bm{m}}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-\Lambda_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty
therefore the limit of the product is the product of the limit and we obtain that 
	\sum_{m=0}^{L}  (\Lambda_{\bm{m}}-H)\lim_{\epsilon\to 0}\epsilon R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0
Since the limit of the sum is the sum of the limit we have   
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
thus 
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
Since $H_{0}=H_{0}^{T}$ 
	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
By calling 
\begin{equation}\label{W-extended}
	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
we finally obtain 
	WH_{0}=HW
Power expanding the transfer matrix by charges and considering the limit for $x\to\infty$ we have that 
		W&= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|\\&=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}-\mathcal{Q}_{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
and also satisfies \eqref{GoalWQ}. We now write the power expansion with respect to $B_{i}^{2L-1}$ of $W$. We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},
	W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
	\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
we further observe that in the limit for $\epsilon\to 0$ the quantity 
\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle
therefore we have that 
		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)
		|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

%Then, we obtain the correspondent transfer matrix as
%\begin{equation}
%	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
%\end{equation}
%where
%\begin{equation}
%	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
%\end{equation}
{\color{blue}
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
\begin{equation}
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}

@@

\paragraph{Genearlization to $N$ species:} we can generalize the eigenvector formula for arbitrary number of species $N>2$ by writing
\begin{equation}
	\begin{split}
	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{2},\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
	\end{split}
\end{equation}
Denoting by
\begin{equation}
A_{j}=	\left\{\left((2x+N)(\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
\end{equation}
the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
\begin{equation}
	\begin{split}
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
\\&
\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=\,k_{q}\}}\right)
\\&
\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
	\end{split}
\end{equation}
Condition \eqref{cond4} becomes
\begin{equation}\label{cond4General}
	G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
\end{equation}
Arguing as in the case $N=3$ we observe that 
\begin{equation}
	\begin{split}
		A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
	\\&
	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{(k_{2}+\cdots+k_{N})}^{q}=k_{q}\}}\right)
	\\&
	\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
	\end{split}
\end{equation}
therefore \eqref{cond4General} is fulfilled. Again, the equivalent of conditions \eqref{cond1}, e\eqref{cond5} and \eqref{cond6} are trivially satisfied. The equivalents of conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{j}(x)$ are rising operators for all $j\in \{2,\ldots,N\}$. }
